Spatial phylogenetics of Japanese ferns: Patterns, processes, and implications for conservation

### 2021-12-27 ms/manuscript.Rmd
Update MS

A necessary step in any analysis of biodiversity is to set the grain size used to accurately define communities (co-occurring species). 
Here, one must consider that smaller grain size is needed to detect environmental effects, while larger grain size is needed to ensure adequate species sampling. 
We created sets of 10 km, 20 km, 30 km, and 40 km grid-cells covering Japan using a Mollweide equal-area projection (size refers to the length of the side of each square grid-cell).
At each grain size, species occurrences were converted to a presence-absence community matrix (a species was considered present if at least one specimen was recorded in that grid-cell). 
We calculated sampling redundancy [1 - richness/number of specimens; @Garcillan2003] to quantify adequacy of sampling. 
Preliminary analysis indicated that 20 km grid-cells are optimal for our dataset (`r s_figure("grain-size")`). 
Although the grid-cells are defined with equal area, actual land area of each cell varies due to presence of coastlines, etc.
Strictly filtering out all grid-cells with less than complete land area would result in a large loss of data, as Japan has many coastlines and small islands.
Therefore, we instead filtered the grid-cells by sampling completeness, removing any cells with redundancy < 0.1; this dataset was used for all subsequent analyses.
The R package `r pack("sf")` was used for all GIS analyses [@Pebesma2018].

>>>>

A necessary step in any analysis of biodiversity is to set the grain size used to accurately define communities (co-occurring species). 
Here, one must consider that smaller grain size is needed to detect environmental effects, while larger grain size is needed to ensure adequate species sampling. 
We created sets of 10 km, 20 km, 30 km, and 40 km grid-cells covering Japan using a Mollweide equal-area projection (size refers to the length of the side of each square grid-cell).
At each grain size, species occurrences were converted to a presence-absence community matrix (a species was considered present if at least one specimen was recorded in that grid-cell). 
We calculated sampling redundancy [1 - richness/number of specimens; @Garcillan2003] to quantify adequacy of sampling. 
Preliminary analysis indicated that 20 km grid-cells are optimal for our dataset: there is a sudden improvement in redundancy values from 10 km to 20 km, but much less improvement as grain size is increased beyond 20 km (`r s_figure("grain-size")`).
Although the grid-cells are defined with equal area, actual land area of each cell varies due to presence of coastlines, etc.
Strictly filtering out all grid-cells with less than complete land area would result in a large loss of data, as Japan has many coastlines and small islands.
Therefore, we instead filtered the grid-cells by sampling completeness, removing any cells with redundancy < 0.1; this dataset was used for all subsequent analyses.
The R package `r pack("sf")` was used for all GIS analyses [@Pebesma2018].
